---
title: "Australia state prison sentence"
author: "Bryan Shalloway"
date: "4/26/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(broom)
library(fpp2)
```

# Prep exmaple dataset

*Prep data used in examples:*
```{r}
prison_df <- fpp2::prisonLF %>% 
  group_by(state, legal, t) %>% 
  summarise(count = sum(count)) %>% 
  ungroup() %>% 
  rename(state_aus = state, date_mo = t) %>% 
  select(state_aus, date_mo, legal, count) %>% 
  arrange(date_mo) %>% 
  spread(legal, count)

```

# List columns example

*Make custom lm function with formula specified:*
```{r}
lm_prison <- function(df){
  lm(Sentenced ~ Remanded, data = df)
}
```

*Unnest evaluation metrics and plot:*
```{r}
prison_df %>%
  group_by(state_aus) %>%
  nest() %>% print() %>% 
  mutate(models = map(data, lm_prison)) %>% print() %>% 
  mutate(eval_metrics = map(models, broom::glance)) %>% print() %>% 
  unnest(eval_metrics, .drop = TRUE) %>% print() %>% 
  ggplot(aes(x = fct_reorder(state_aus, r.squared),
             y = r.squared)) +
  geom_col()
```

* print statements show output at each step for use in presentation

*Build dataframe and print particular elements:*
```{r}
core_data <- prison_df %>% 
  group_by(state_aus) %>% 
  nest() %>% 
  mutate(models = map(data, lm_prison)) %>% 
  mutate(eval_metrics = map(models, broom::glance))

core_data %>% 
  pluck("data", 1)

core_data %>% 
  pluck("models", 1)

core_data %>% 
  pluck("eval_metrics", 1)
```

* extract objects and paste into presentation

# Cluttered environment example

Run below and then take screenshot of "cluttered" environment for presentation.

```{r}
knitr::opts_chunk$set(eval = FALSE)
```


*Visualization:*
```{r}
chart <- prison_df %>% 
  ggplot(aes(x = Remanded, y = Sentenced))+
  geom_point()
  # facet_wrap(~state_aus, scales = "free")

chart1 <- chart
chart2 <- chart
chart3 <- chart
chart4 <- chart
```

```{r}
charts_mult <- prison_df %>% 
  ggplot(aes(x = Remanded, y = Sentenced, colour = state_aus))+
  geom_point()

map(1:8, 
     ~charts_mult +
      ggforce::facet_wrap_paginate(~state_aus, ncol = 1, nrow = 1, scales = "free", page = .x)+
      theme(legend.position = "none") 
     )
```

*Model:*
```{r}
model <- lm(Sentenced ~ Remanded, data = prison_df)

model_simple %>% 
  summary()

model1 <- model
model2 <- model
model3 <- model
model4 <- model

```

```{r}
valuation_metrics <- model %>% 
  broom::glance()

evaluation_metrics1 <- evaluation_metrics
evaluation_metrics2 <- evaluation_metrics
evaluation_metrics3 <- evaluation_metrics
evaluation_metrics4 <- evaluation_metrics
```